Digital History in Finland, 1488-1828

### 2016-07-02 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@

for (pn in names(x)) {
  fnam <- gsub(",", "", gsub(" ", "_", pn))
  write_xtable(x[[pn]], file = paste(output.folder, "subjecttopics", fnam, ".tab", sep = ""))
}
```

>>>>

PUBLISHER-TODO: julkaisijakuvat jotka edellä, samat kuin Fennica Kungligalle.

@@

for (pn in names(x)) {
  fnam <- gsub(",", "", gsub(" ", "_", pn))
  write_xtable(x[[pn]], file = paste(output.folder, "subjecttopics", fnam, ".tab", sep = ""))
}
```
PUBLISHER-TODO: julkaisijakuvat jotka edellä, samat kuin Fennica Kungligalle.
